---
title: "PA1_template.Rmd"
output: html_document
---

```{r, echo=FALSE}
setwd("/home/bala/Downloads/reproducible_research/peer1_assesment")

orig_data<-read.csv("activity.csv")

data<-orig_data[!(is.na(orig_data$steps)),]

aggr_data<-aggregate(data$steps,by=list(date=data$date),FUN="sum")
```
Make a histogram of the total number of steps taken each day
```{r, echo=FALSE}
plot(aggr_data$x,type="h",main="Total number of steps taken each day",xlab="Dates",ylab="Steps Per Day")
```

Calculate and report the mean and median total number of steps taken per day
```{r, echo=FALSE}
mean_data<-aggregate(data$steps,by=list(date=data$date),FUN="mean")
median_data<-aggregate(data$steps,by=list(date=data$date),FUN="median")
```
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r, echo=FALSE}
plot(mean_data$x,type="l",main="Total number of steps taken each day",xlab="Dates",ylab="Steps Per Day")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r, echo=FALSE}
max_steps<-aggregate(data$steps,by=list(interval=data$interval),FUN="mean")
which.max(max_steps[,2])
```

Counting the NA values in the dataset
```{r, echo=FALSE}
sum(is.na(orig_data))
```
Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
```{r, echo=FALSE}
orig_data$day <- as.POSIXlt(orig_data$date)$wday

orig_data$day[orig_data$day == 1]  <- "Weekday" 
orig_data$day[orig_data$day == 2]  <- "Weekday" 
orig_data$day[orig_data$day == 3]  <- "Weekday" 
orig_data$day[orig_data$day == 4]  <- "Weekday" 
orig_data$day[orig_data$day == 5]  <- "Weekday" 
orig_data$day[orig_data$day == 6]  <- "Weekend" 
orig_data$day[orig_data$day == 0]  <- "Weekend"

```